---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
```

# Lab report #1

<<<<<<< HEAD
=======
## Question 1:

```{r}
str(ames)
?ames
```

The variables are:\
- Parcel ID: a chr variable that is a character ID number.\
- Address: a chr variable that holds the property address in Ames, IA\
- Style: factor variable detailing the type of housing\
- Occupancy: factor variable of the type of housing\
- Sale Date: date in chr format that is the date of house sale\
- Sale Price: a numerical variable that holds the sales price (in US dollar)\
- Multi Sale: a chr that is a value if the sale was part of a package and null if not\
- YearBuilt: an integer variable that hold the year that the house was built\
- Acres: a numerical variable that holds the acres of the lot that the house is built on\
- TotalLivingArea: a numerical variable of the total living are in square feet\
- Bedrooms: a numerical variable that tells the number of bedrooms\
- FinishedBsmtArea: a numerical value that tells the total area of the finished basement in square feet and is null if the basement is not finished\
- LotArea: a numerical variable that is the total lot area in square feet\
- AC: a chr variable that is either "Yes" or "No" depending on if the property has AC or not\
- FirePlace: a chr variable that is either "Yes" or "No" depending on if the property has a fireplace or not\
- Neighborhood: a factor variable, where the levels indicate neighborhood are in Ames

## Question 2

A variable that seems the most important is "sale Price". When drawing conclusions from this data, the most useful application I believe would be predicting prices of homes with this variable. So it makes sense for Sale Price to be our main variable.(Andrew)

## Question 3 (Vanessa):

```{r}
library(classdata)
View(ames)
```

Range of the Variable:

```{r}
summary(ames$`Sale Price`)
```

Histogram: There is something odd about the histogram, as it appears to show sale prices of 0s.

```{r}
library(ggplot2)
ggplot(ames, aes( x=`Sale Price`)) + geom_histogram(binwidth = 10000000)
```


<<<<<<< HEAD
=======
## Question 4:

### Emily Maruska - Finished Basement Area
```{r}
summary(ames$`FinishedBsmtArea (sf)`)
ggplot(ames, aes(x = ames$`FinishedBsmtArea (sf)`)) + geom_histogram()
```
There is a distinct pattern in the histogram that shows that most of the houses that have a finished basement have a basement area that is roughly around 1000 square feet. There are, however, a few houses that have extremely large basements in comparison.
```{r}
ggplot(ames, aes(x = ames$`FinishedBsmtArea (sf)`, y = ames$`Sale Price`)) + ylim(0, 1300000) + geom_point()
```  

In comparing the finished basement area to the sales price, there is a pretty clear pattern that generally the larger the finished basement, the larger the sales price is. There are a decent amount of outliers, such as houses that sold for very little cost but with a finished basement are of roughly 2000, or houses that sold for an extremely high cost with a finished basement of 2000 as well. This also reflects the oddities found in question 3 as there are also many values in this scatter plot that indicate a finished basement in a house that sold for no cost.  


### Vanessa Ramirez - Lot Area (sf)
Range: Min: 0 and Max: 523228  
```{r}
summary(ames$`LotArea(sf)`)
```

Scatterplot: 
There is no relationship between sales price and lot area.It seems that both the lot area
and sale price are recorded as 0, which is why most of the points are clustered together 
in the bottom left corner. 
```{r}
ggplot(data = ames) + geom_point(mapping = aes(x = `LotArea(sf)`, 
                                               y = `Sale Price`)) + 
  labs(x = "Lot Area (sf)" , 
       y = " Sale Price")
```
















<<<<<<< HEAD
=======




### Andrew Kinneer - Year Built
For my variable I chose "YearBuilt"
```{R}
range(ames$YearBuilt, na.rm = TRUE)
```
The range of this variable is from 0 - 2022
Here is the distribution of YearBuilt. There are a few outliers at 0 which are removed in the chart
```{R}
library(ggplot2)
ggplot(ames, aes(x = YearBuilt)) +
  geom_bar(binwidth = 10,color = "skyblue") +
  labs(title = "Count of YearBuilt", x = "Year", y = "Count") +
  xlim(1880, 2022)
```

Below you can see the comparison of YearBuilt to SalePrice. At first there seems to be no increase in SalePrice over the years. At around 1960 there became a general increase in SalePrice with it peaking in the current year. This does not explain the previous oddities mentioned in #3 with the zeros.

```{R}
ggplot(ames, aes(x = YearBuilt, y = `Sale Price`)) +
  geom_point(color = "blue", alpha = 0.7) +
  labs(title = "Scatter Plot of YearBuilt vs Sale Price",
       x = "Year Built",
       y = "Sale Price") +
  xlim(1880, 2022) +
  ylim(1, 1500000)
```


Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.
