---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(classdata)
```

# Lab report #1

<<<<<<< HEAD
=======
## Question 1:

```{r}
str(ames)
?ames
```

The variables are:\
- Parcel ID: a chr variable that is a character ID number.\
- Address: a chr variable that holds the property address in Ames, IA\
- Style: factor variable detailing the type of housing\
- Occupancy: factor variable of the type of housing\
- Sale Date: date in chr format that is the date of house sale\
- Sale Price: a numerical variable that holds the sales price (in US dollar)\
- Multi Sale: a chr that is a value if the sale was part of a package and null if not\
- YearBuilt: an integer variable that hold the year that the house was built\
- Acres: a numerical variable that holds the acres of the lot that the house is built on\
- TotalLivingArea: a numerical variable of the total living are in square feet\
- Bedrooms: a numerical variable that tells the number of bedrooms\
- FinishedBsmtArea: a numerical value that tells the total area of the finished basement in square feet and is null if the basement is not finished\
- LotArea: a numerical variable that is the total lot area in square feet\
- AC: a chr variable that is either "Yes" or "No" depending on if the property has AC or not\
- FirePlace: a chr variable that is either "Yes" or "No" depending on if the property has a fireplace or not\
- Neighborhood: a factor variable, where the levels indicate neighborhood are in Ames

## Question 2

A variable that seems the most important is "sale Price". When drawing conclusions from this data, the most useful application I believe would be predicting prices of homes with this variable. So it makes sense for Sale Price to be our main variable.(Andrew)

## Question 3 (Vanessa):

```{r}
library(classdata)
View(ames)
```

Range of the Variable:

```{r}
summary(ames$`Sale Price`)
```

Histogram: There is something odd about the histogram, as it appears to show sale prices of 0s.

```{r}
library(ggplot2)
ggplot(ames, aes( x=`Sale Price`)) + geom_histogram(binwidth = 10000000)
```


<<<<<<< HEAD
=======
## Question 4:

### Emily Maruska - Finished Basement Area


















Follow the instructions posted at <https://ds202-at-isu.github.io/labs.html> for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.

All submissions to the github repo will be automatically uploaded for grading once the due date is passed. Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.
